13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2019-03-22 rules/rules19.tex
Add initial version of rules 2019 document.

\newcommand{\akey}[1]{\textbf{#1}}

@@

\author{%
Matthias Heizmann \\
University of Freiburg \\
Germany \\
{\small\href{mailto:heizmann@informatik.uni-freiburg.de}{\texttt{heizmann@informatik.uni-freiburg.de}}} \\
\and
Aina Niemetz \\
Stanford University\\
USA\\
{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
\and
Giles Reger \\
University of Manchester \\
UK \\
{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
\and
Tjark Weber \\
Uppsala University \\
Sweden \\
{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
\\
}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org} or
\url{smtcomp.sourceforge.net/2018}.

@@

\begin{description}
\item[April~8] Deadline for new benchmark contributions.
\item[May~15] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~10] Deadline for final versions of solvers, including
  system descriptions.
\item[June~11] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~12/13] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2018 is part of the SMT Workshop~2018
(\url{http://smt-workshop.cs.uiowa.edu/2018/}),
which is affiliated with IJCAR~2018 (\url{http://ijcar2018.org/}),
part of FLoC 2018 (\url{http://www.floc2018.org/}).
The SMT Workshop will include a block of time to present the results of the
competition.

@@

SMT-COMP 2018 will have three tracks: the conventional main track, an
application (i.e., incremental) track, and an unsat-core track.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the main track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the main track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

@@

As part of the FLoC Olympic Games, medals will be awarded to:
%
\begin{itemize}
\item The best three solvers according to the competition-wide scoring
  (main track);
\item the solver that wins the most competitive divisions in the
  application track;
\item the solver that wins the most competitive divisions in the
  unsat-core track;
\item the solver that wins the QF\_BV division (separately for
  parallel and sequential performance) in the main track.
\end{itemize}

>>>>

\newcommand{\akey}[1]{\textbf{#1}}
\newcommand{\todo}[1]{\textcolor{red}{[#1]}}

@@

\author{%
Liana Hadarean \\
Amazon \\
USA \\
{\small\href{mailto:hadarean@amazon.com}{\texttt{hadarean@amazon.com}}}\\
\and
Antti Hyvarinen \\
Universita della Svizzera italiana \\
Switzerland \\
{\small\href{mailto:tjark.weber@it.uu.se}{\texttt{tjark.weber@it.uu.se}}} \\
\and
Aina Niemetz \\
Stanford University\\
USA\\
{\small\href{mailto:niemetz@cs.stanford.edu}{\texttt{niemetz@cs.stanford.edu}}}\\
\and
Giles Reger \\
University of Manchester \\
UK \\
{\small\href{mailto:giles.reger@manchester.ac.uk}{\texttt{giles.reger@manchester.ac.uk}}} \\
\\
}

@@

\noindent Additional material will be made available at the
competition web site, \url{www.smtcomp.org}.

@@

\begin{description}
\item[March~1] Deadline for new benchmark contributions.
\item[May~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~19] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~2] Deadline for final versions of solvers, including
  system descriptions.
\item[\todo{TODO}] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~7/8] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2019 is part of the SMT Workshop~2019
(\url{http://smt2019.galois.com/}),
which is affiliated with SAT~2019 (\url{http://sat2019.tecnico.ulisboa.pt/}).
The SMT Workshop will include a block of time to present the results of the
competition.

@@

SMT-COMP 2019 will have four tracks: the single problem track (formerly
known as main track), the incremental track (formerly known as application
track), the unsat-core track, and the (new) industry challenge track.

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
	and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2019.
\todo{update changes vs 2018}
The principal changes from the previous competition rules are the following:
\begin{itemize}
\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the main track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the main track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

@@

As part of the FLoC Olympic Games, Kurt G{\"o}del medals will be
awarded to:
%
\begin{itemize}
\item The best three solvers according to the competition-wide scoring
  (main track);
\item the solver that wins the most competitive divisions in the
  application track;
\item the solver that wins the most competitive divisions in the
  unsat-core track;
\item the solver that wins the QF\_BV division (separately for
  parallel and sequential performance) in the main track.
\end{itemize}
